\documentclass[a4paper,11pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% Page Geometry
\geometry{left=2cm, right=2cm, top=2cm, bottom=2cm}

% Hyperlink Setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    pdftitle={Resume},
    pdfauthor={Sivasai}
}

% Custom Commands
\newcommand{\resumeline}{\noindent\rule{\linewidth}{0.4pt}}

% Section Formatting
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\resumeline\vspace{0.2cm}]
\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1.3ex plus .2ex}
\pagestyle{empty} % No page numbers

% Data (from resume_builder.py)
\newcommand{\fullname}{Sivasai}
\newcommand{\jobtitle}{Freelance Web Developer & Designer}
\newcommand{\phone}{+1-234-567-890}
\newcommand{\email}{sivasai@example.com}
\newcommand{\linkedin}{linkedin.com/in/sivasai}
\newcommand{\github}{github.com/sivasai}
\newcommand{\website}{sivasai.dev}
\newcommand{\address}{Bangalore, India}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{\fullname}}
    \vspace{0.1cm}
    \resumeline
    \vspace{0.1cm}
    {\large \textit{\jobtitle}}
    \vspace{0.1cm}
    \href{tel:\phone}{\phone} • \href{mailto:\email}{\email} • \href{https://\linkedin}{\linkedin} • \href{https://\github}{\github} • \href{https://\website}{\website} • \address
\end{center}

% --- PROFESSIONAL SUMMARY ---
\section*{Professional Summary}
Highly motivated and versatile professional with experience in freelance web development, digital content creation, and project management. Skilled in developing custom WordPress sites, designing engaging marketing visuals, and executing end-to-end project delivery. Proven ability to grow online presence through SEO-friendly content and strategic social media marketing. Seeking to leverage technical and creative skills in a challenging new role.

% --- SKILLS ---
\section*{Skills}
\begin{itemize}[leftmargin=*, label={}]
    \item \textbf{Programming:} Python, JavaScript, HTML5, CSS3, SQL
    \item \textbf{Frameworks & Libraries:} React, Node.js, Django, Flutter
    \item \textbf{Databases:} MySQL, PostgreSQL, MongoDB, Firebase
    \item \textbf{Tools / Platforms:} Git, Docker, WordPress, Adobe Creative Suite, SEO Tools
\end{itemize}

% --- EDUCATION ---
\section*{Education}
\textbf{Bachelor of Technology in Computer Science} \hfill 2022 -- 2026 \\
\textit{Vellore Institute of Technology, Vellore, India} \\
Relevant Courses: Data Structures and Algorithms, Object-Oriented Programming, Database Management Systems, Web Development.

% --- EXPERIENCE ---
\section*{Experience}
\textbf{Freelance Web Developer & Designer} \hfill 2022 -- 2026 \\
\textit{Edutech, Bangalore}
\begin{itemize}[leftmargin=*, topsep=0.2cm, itemsep=0pt, parsep=0pt]
    \item Developed custom WordPress websites for businesses and individuals.
    \item Designed engaging graphics, social media creatives, and marketing visuals.
    \item Edited and produced YouTube & Instagram Reels for e-commerce and business promotion.
    \item Managed end-to-end project execution including client communication, design, development, and delivery.
\end{itemize}

\vspace{0.2cm}
\textbf{Digital Content Creator} \hfill 2022 -- 2025 \\
\textit{Tech Andhra, Andhra Pradesh}
\begin{itemize}[leftmargin=*, topsep=0.2cm, itemsep=0pt, parsep=0pt]
    \item Created SEO-friendly blog content and social media posts in both Telugu and English.
    \item Grew online presence for brands through Instagram, YouTube, and Facebook marketing.
\end{itemize}

\vspace{0.2cm}
\textbf{Digital Content Creator} \hfill 2025 -- Present \\
\textit{Tech Term, Bangalore}
\begin{itemize}[leftmargin=*, topsep=0.2cm, itemsep=0pt, parsep=0pt]
    \item Created SEO-friendly blog content and social media posts in both Telugu and English.
    \item Grew online presence for brands through Instagram, YouTube, and Facebook marketing.
\end{itemize}

% --- PROJECTS ---
\section*{Projects}
\textbf{Telugu Career Path Job Updates Website} \hfill 2020 -- 2022\\
\textit{Outcome: High user engagement; key resource for local job seekers.}
\begin{itemize}[leftmargin=*, topsep=0.2cm, itemsep=0pt, parsep=0pt]
    \item Developed a WordPress-based job portal using GeneratePress Scribe theme.
    \item Implemented SEO and responsive UI to increase reach.
    \item Streamlined content workflows for job alerts and resources.
\end{itemize}

\vspace{0.2cm}
\textbf{Resumate Quantum Forge AI Resume Builder} \hfill 2023 -- 2024\\
\textit{Outcome: Demonstrated AI integration and full-stack development skills.}
\begin{itemize}[leftmargin=*, topsep=0.2cm, itemsep=0pt, parsep=0pt]
    \item Built an AI-powered resume generator using Streamlit and Google Gemini API.
    \item Added ATS scoring, grammar enhancement, and guided inputs.
\end{itemize}

\vspace{0.2cm}
\textbf{Local Grocery Delivery App (Flutter + Firebase)} \hfill 2024 -- 2025\\
\textit{Outcome: Launched a practical solution for local community needs.}
\begin{itemize}[leftmargin=*, topsep=0.2cm, itemsep=0pt, parsep=0pt]
    \item Created a mobile app for village-level grocery and milk delivery.
    \item Built product listing, cart, and order tracking.
    \item Designed simple UI for non-technical users.
\end{itemize}

% --- CERTIFICATES ---
\section*{Certificates}
\textbf{Google Certified Digital Marketer} - Google, 2023 \\
\textbf{Advanced SEO Certification} - HubSpot, 2022

% --- ACHIEVEMENTS ---
\section*{Achievements}
\textbf{Winner, National Hackathon 2024}: Developed an award-winning solution for sustainable tech. \\
\textbf{Top Rated Freelancer}: Maintained a 5-star rating on Upwork for over 50 projects.

% --- LANGUAGES ---
\section*{Languages}
English (Fluent), Telugu (Native)

\end{document}
